Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
fix title paragraph nn consensus

\paragraph{K-Nearest Neighboring Consensus}
In case of homogeneous agents (i.e., when all agents have the same action and observation space),
the goal of learning is to find a common policy that all agents can follow.
This approach is typically used in large-scale systems where agents are identical and need to reach a consensus---see~\cite{DBLP:conf/eusipco/BaldazoPZ19}.
%
In this case, instead of forcing a common policy, we can let agents learn independently and then select the best-performing agent as the reference for the others, leading eventually to a consensus on the best same policy.
%
In this way, each agent $i$ continue to learn independently, but at each iteration, it updates its Q-network using the Q-values of the best-performing agent in its neighborhood.
%
The best performing agent is selected based on the average reward it has received in the last $n$ episodes.
Formally, the update rule for agent $i$ at time $t+1$ is:
\begin{equation}
  \theta^{t+1}_i \leftarrow \theta^t_{\text{best}}
\end{equation}
where $\theta^t_{\text{best}}$ is the Q-network of the best-performing agent in the neighborhood $\mathcal{N}_k(i)$ at time $t$.

>>>>

\paragraph{K-Nearest Neighbor Consensus}
In case of homogeneous agents (i.e., when all agents have the same action and observation space),
the goal of learning is to find a common policy that all agents can follow.
This approach is typically used in large-scale systems where agents are identical and need to reach a consensus---see~\cite{DBLP:conf/eusipco/BaldazoPZ19}.
%
In this case, instead of forcing a common policy, we can let agents learn independently and then select the best-performing agent as the reference for the others, leading eventually to a consensus on the best same policy.
%
In this way, each agent $i$ continue to learn independently, but at each iteration, it updates its Q-network using the Q-values of the best-performing agent in its neighborhood.
%
The best performing agent is selected based on the average reward it has received in the last $n$ episodes.
Formally, the update rule for agent $i$ at time $t+1$ is:
\begin{equation}
  \theta^{t+1}_i \leftarrow \theta^t_{\text{best}}
\end{equation}
where $\theta^t_{\text{best}}$ is the Q-network of the best-performing agent in the neighborhood $\mathcal{N}_k(i)$ at time $t$.
